Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-14 paper/agree.tex
minor textual stuff
Revise example and add TODOs in all sections

\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree]
eq req : bool = event(AutomationRequest);
eq avl : bool = event(AirVehicleLocation);
eq wp : bool = event(Waypoint);
eq rsp: bool = event(Start);
eq alrt : bool = event(Alert);

assume "Automation request is well-formed" :
    req => WELL_FORMED_AUTOMATION_REQUEST(AutomationRequest);
assume "Air vehicle location is well-formed" :
    avl => WELL_FORMED_WAYPOINT(AirVehicleLocation);

eq current : bool = (req = rsp);
eq previous : bool = (req and not rsp) ->
                      pre(req and not rsp) and (not req and rsp);
eq policy : bool = current or previous;
eq since : bool =  alrt or (alrt and (false -> pre(since)));

guarantee "Start includes a waypoint" :
    rsp => wp;
guarantee "Locations required after the start waypoint" :
    (wp and not rsp) => avl;
guarantee "Waypoint is well-formed" :
    wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Alert if start is not bounded relative to a request" :
    policy or since;
\end{lstlisting}
\end{lrbox}

\begin{figure}
  \begin{center}
    \scalebox{0.60}{\usebox{\sw}}
  \end{center}
  \caption{The SW component contract.}
  \label{fig:sw}
\end{figure}

@@

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree]
eq policy : bool =
  WELL_FORMED_AUTOMATION_RESPONSE(Input);
guarantee Filter_Output "Filter output is well-formed" :
  if event(Input) and policy then
    event(Output) and Output = Input
  else not event(Output);
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree]
const is_latched : bool =
  Get_Property(this, CASE_Properties::Monitor_Latched);
eq rsp : bool = event(Response);
eq req : bool = event(Request);
eq current : bool = (req = rsp);
eq previous : bool = (req and not rsp) ->
                      pre(req and not rsp) and (not req and rsp);
eq policy : bool = current or previous;
eq alert : bool = (not policy)
                -> ((is_latched and pre(alert)) or not policy);
guarantee Monitor_Alert
  "Alert port tracks alert variable" :
  event(Alert) = alert;
guarantee Monitor_Output
  "Output if not alerted" :
  if event(Alert) then (not event(Output)) else
  if event(Response) then (event(Output) and (Output = Response))
  else (not event(Output));
\end{lstlisting}
\end{lrbox}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \scalebox{0.60}{\usebox{\flt}} \\
      (a) \\
      \scalebox{0.60}{\usebox{\mntr}} \\
      (b)
    \end{tabular}
  \end{center}
  \caption{High-assurance component contracts. (a) The filter. (b) The monitor.}
  \label{fig:assurance}
\end{figure}

@@

The AGREE contract specification generated by the transform is shown in \figref{fig:assurance}(a).
The guarantee is stylized for synthesis and completely defines the meaning of the output under every possible input.
The resulting AGREE specification for the monitor in this example is shown in \figref{fig:assurance}(b).
The \texttt{is\_latched} value makes the alert persistent, meaning that once the alert is raised, it is always raised.
This behavior is one of the several options available in the dialogue.
The definition for \texttt{policy} is taken by the system developer from the contract in \figref{fig:sw}.
As before, the guarantees for the outputs are autogenerated by the tool and completely define each output under every possible input.

>>>>

\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree,numbers=left]
eq req : bool = event(AutomationRequest);
eq avl : bool = event(AirVehicleLocation);
eq wp : bool = event(Waypoint);
eq strt: bool = event(Start);
eq alrt : bool = event(Alert);

assume "Automation requests are well-formed" :
  req => WELL_FORMED_AUTOMATION_REQUEST(AutomationRequest);
assume "Air vehicle locations are well-formed" :
  avl => WELL_FORMED_WAYPOINT(AirVehicleLocation);    
assume "One automation request in flight at a time" :
  true -> 
  (req => pre(Historically(not req) or Since(not req, strt)));

guarantee "Waypoints coincide with air vehicle locations":
  wp => avl;
guarantee "Starts include a new waypoint" :
  strt => wp;
guarantee "Waypoints are well-formed" : 
  wp => WELL_FORMED_WAYPOINT(Waypoint);
guarantee "Starts within one cycle of requests if not alerting" :
  (strt => ((not alrt) and req)) -> 
  (strt => ((not alrt) and (req or pre(req))));
guarantee "Alert if not started within one cycle of requests" :
    true -> ((pre(req and not strt) and not strt) => alrt);
guarantee "Once alerted always alerted" :
  not alrt or (Once(alrt) and alrt);
\end{lstlisting}
\end{lrbox}

\begin{figure}
  \begin{center}
    \scalebox{0.62}{\usebox{\sw}}
  \end{center}
  \caption{The SW component contract.}
  \label{fig:sw}
\end{figure}

@@

\newsavebox{\flt}
\begin{lrbox}{\flt}
\begin{lstlisting}[style=agree,numbers=left]
eq policy : bool = 
  WELL_FORMED_AUTOMATION_RESPONSE(Input);

guarantee Filter_Output
  "Filter output is well-formed" :
  if event(Input) and policy then 
    event(Output) and Output = Input
  else not event(Output);
\end{lstlisting}
\end{lrbox}

\newsavebox{\mntr}
\begin{lrbox}{\mntr}
\begin{lstlisting}[style=agree,numbers=left]
const is_latched : bool = true;
const MAX_LATENCY : int = 1;

eq rsp : bool = event(Response);
eq req : bool = event(Request);

eq isPending : bool = Since(not rsp, req and not rsp);
eq latency : int = 0 -> (if req then 0 else pre(latency) + 1);

eq policy : bool = (rsp => req) ->
                   (    (isPending => latency < MAX_LATENCY)   
                    and (rsp => (req or pre(isPending))));
eq alert : bool = (not policy) -> 
                  ((is_latched and pre(alert)) or not policy);

assume "One outstanding request at a time" :
  (true -> (req => not pre(isPending)));

guarantee "Alert port tracks alert variable" :
  event(Alert) = alert;
guarantee "Output if not alerted" :
  if (not(alert) and rsp) then
    event(Output) and (Output = Response)
  else
    not (event(Output));    
\end{lstlisting}
\end{lrbox}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \scalebox{0.62}{\usebox{\flt}} \\
    \end{tabular}
  \end{center}
  \caption{Contract specification for high-assurance filter.}
  \label{fig:filter}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \scalebox{0.62}{\usebox{\mntr}} \\
    \end{tabular}
  \end{center}
  \caption{Contract specification for high-assurance monitor.}
  \label{fig:monitor}
\end{figure}

@@

The AGREE contract specification generated by the transform is shown in \figref{fig:filter}.
The guarantee is stylized for synthesis and completely defines the meaning of the output under every possible input.
The resulting AGREE specification for the monitor in this example is shown in \figref{fig:monitor}.
The \texttt{is\_latched} value makes the alert persistent, meaning that once the alert is raised, it is always raised.
This behavior is one of the several options available in the dialogue.
The definition for \texttt{policy} is taken by the system developer from the contract in \figref{fig:sw}.
As before, the guarantees for the outputs are autogenerated by the tool and completely define each output under every possible input.

### 2022-03-14 paper/example.tex
Revise example and add TODOs in all sections

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{example.png} \\
      (a) \\
      \includegraphics[scale=0.4]{example-certificate.png} \\
      (b)
    \end{tabular}
  \end{center}
\caption{Automated UAV route planning system. (a) Unhardened system. (b) Failure certificate.}
\label{fig:example}
\end{figure*}

\figref{fig:example} is an AADL architectural model of a software system (SW) for route planning and automated control of a UAV. It is loosely based on the system in the case study introduced in Section~\ref{sec:case-study}.  The source for the entire model is found at \cite{repo}. The system receives an automation request that is forwarded to an untrusted third-party route planner (AI).  The route planner decides the flight path of the UAV based on its current position and the requested task. The waypoint manager (WM) receives the mission command as a set of waypoints from the planner and starts the UAV flying the mission, issuing waypoints to the UAV flight controller as the UAV location changes. The waypoint manager is an \emph{as is} legacy component.

The expected behavior of the SW system, and the components in its implementation, are modeled with AGREE contract specifications. The contracts constrain input and state properties of output for component models. AGREE performs model checking on this assume-guarantee system to hierarchically prove that the composite system obeys all contract obligations under all possible finite input streams.

The initial AGREE contract specifications for the components and the overall system make no assumptions about the integrity of the inputs and outputs. A cyber-vulnerability analysis identifies the potential of the untrusted AI route planner component to behave maliciously. In response, the developer modifies the AGREE specification for the AI route planner to model this ability to behave maliciously as an untrusted component by removing any guarantees about its output.  In other words, the AI output is unconstrained in the AGREE specification, allowing it to take on any value and allowing the AI component to send that value at any time.

The contract specifications for the other components are also updated with the threat analysis information by adding in new requirements to mitigate the identified cyber-vulnerabilities. For example, a designer adds to the specification for the legacy waypoint manager assumptions about its input being \emph{well-formed} since that is no longer known \emph{a priori} as the AI route planner output is unconstrained. The systems designer is also responsible for defining the meaning of ``well-formed''; in this example, it is a predicate checking that the waypoints are within bounded value ranges for latitude, longitude, and altitude, with an additional integrity check on message IDs.

The developer adds two other requirements to the SW AGREE specification related to the cyber-vulnerability analysis.  The first, \emph{Waypoint is well-formed} requires all the waypoints sent to the UAV flight controller to be well-formed (it detects if malformed waypoints are propagated downstream).  The second, \emph{Alert if start is not bounded relative to a request}, requires an automation request to correspond with an automation response either in the same step or within one step (it detects if a mission is being started without a request or if the start is delayed more than one step after a request). The goal of these two requirements is to detect if the untrusted component is trying to prevent the UAV from flying its intended mission or to fly a wrong mission.

AGREE examines the composition of the new specifications for the implementation in \figref{fig:example}(a) to determine whether it complies with the added cyber requirements, by way of model checking. The output from the model checker is shown in \figref{fig:example}(b). The red exclamation points designate properties that do not hold. Each of these failures comes with a counterexample. The results are not unexpected given the AI route planner's unconstrained behavior and the new assumptions about the wellformedness of the input to the legacy waypoint manager. The counterexample for \emph{Alert if start is not bounded relative to a request} shows a response in the first time step with no matching request, a  clear malicious behavior from the untrusted component.

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.3]{hardened.png} \\
      (a) \\
      \includegraphics[scale=0.4]{hardened-certificate.png} \\
      (b)
    \end{tabular}
  \end{center}
  \caption{Hardened UAV system. (a) The implementation with high-assurance components. (b) Passing certificate.}
  \label{fig:hardened}
\end{figure*}

The system implementation is cyber-hardened using BriefCASE, which automatically transforms the model by inserting high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}(a). A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input violates the filter invariant. The auto-generated AGREE specification states that only well-formed inputs are passed to the output. The system developer must provide this filtering policy, but it is usually based on the existing assumptions made by downstream components that consume the filter output.

@@

The AGREE analysis of the cyber-hardened implementation with the auto-generated high-assurance components is shown in \figref{fig:hardened}(b). Here AGREE provides a proof certificate that the high-assurance components guarantee the correct behavior of the SW implementation in the presence of the considered cyber vulnerabilities from the untrusted AI route planner.

@@

A similar proof is given for the synthesis of the contract model for a high-assurance component to CakeML. A high-assurance component contract has a precise meaning in terms of data streams, and the synthesis exactly preserves that meaning in the generated code. In other words, for any set of input streams that meet the component's contract assumptions, the output streams produced from the synthesized CakeML exactly match the output streams from the high-assurance component's contract.

Preserving the input/output relationship of streams between the two models lifts the contract verification results to the deployed system. If the contract model verification succeeds, then the meaning of those results hold for the deployed system, given that all other components implement their contracts, an appropriate schedule exists that follows the dependent data-flow, and the communication fabric works as expected.

>>>>

\begin{figure*}[h]
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{example.png}
    \end{tabular}
  \end{center}
\caption{Initial design for an automated UAV route planning system.}
\label{fig:example}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{example-certificate.png} \\
    \end{tabular}
  \end{center}
\caption{AGREE failure certificate for initial design.}
\label{fig:example-certificate}
\end{figure}

\figref{fig:example} is an AADL architectural model of a software system (SW) for route planning and automated control of a UAV.
It is loosely based on one of the case studies in Section~\ref{sec:case-study}.
The source for the entire model is found at \cite{repo}.

The system receives an automation request that is forwarded to a third-party route planner (AI).
The route planner decides the flight path of the UAV based on its current position and the requested task.
The waypoint manager (WM) receives the mission command as a set of waypoints from the planner and starts the UAV flying the mission, issuing waypoints to the UAV flight controller as the UAV location changes.
The waypoint manager is a repurposed legacy component that cannot be modified.

The expected behavior of the SW system, and the components in its implementation, are specified (i.e., modeled) with AGREE contract specifications.
The contracts constrain input with assumptions and state properties of output with guarantees.
AGREE performs model checking on this assume-guarantee system to hierarchically prove that the composite system obeys all contract obligations under all possible finite input streams. 
The AGREE contracts for the system and its implementing components are discussed in greater detail in \secref{sec:agree}.

The initial contract for the system in \figref{fig:example}, and its implementing components, assume and guarantee the absence of any malicious, or underspecified, component behavior.
The system assumes that all inputs are \emph{well-formed} and there is never more than one automation request pending at a time.
The meaning of well-formed is given by predicates for each data type.
For example, a waypoint is well-formed if it falls within bounds for latitude, longitude, and altitude.
The system guarantees that a start includes a waypoint, a start is within one cycle of an automation request and if not, then it persistently alerts, new waypoints coincide with air vehicle location updates, and all output are well-formed.

The components assume their inputs are well-formed, and they guarantee their outputs are well-formed.
The AI further guarantees it only responds to automation requests and always in the same cycle.
The legacy WM further guarantees a start from a response and always in the same cycle, start always comes with a waypoint, and further waypoints coincide with air vehicle location updates.
This system implementation passes AGREE verification meaning that the contract composition of the components with the system satisfies all component input assumptions and system output guarantees.

A cyber-vulnerability analysis identifies the potential of a supply chain attack through the AI route planner provided by the third-party vendor without source code.
The component is marked as \emph{untrusted}, and its contract is modified by removing all guarantees on its outputs to reflect its untrusted status.
The AI output is now unconstrained in the assume-guarantee reasoning of AGREE and is able to generate any value on its output stream at anytime.
AGREE must consider all possible output streams from the AI in proving the correctness of the component implementation of the automated UAV route planning system.

The output from AGREE with the AI specification is shown in \figref{fig:example-certificate}.
The red exclamation points designate component assumptions or system output guarantees that do not hold, and each failure comes with a corresponding counter-example.
The results are not unexpected given the AI route planner's unconstrained behavior.

For example, the first violation is that the automation response from the AI to the WM is no longer guaranteed to be well-formed.
The consequence of that failing input assumption is that the WM outputs are no longer guaranteed; they are effectively unconstrained.
These missing output guarantees from the WM lead to the rest of the failures in \figref{fig:example-certificate} because the WM provides the system level outputs.

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.3]{hardened.png}
    \end{tabular}
  \end{center}
  \caption{Cyber-hardened design for an automated UAV route planning system}
  \label{fig:hardened}
\end{figure*}

\begin{figure}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{hardened-certificate.png}
    \end{tabular}
  \end{center}
  \caption{AGREE verification certificate for cyber-hardened design.}
  \label{fig:hardened-certificate}
\end{figure}

The system implementation is cyber-hardened using BriefCASE, which automatically transforms the model by inserting high-assurance components in the form of a filter and a monitor as shown in \figref{fig:hardened}.
A filter enforces an invariant over each datum in the data stream by not forwarding input to its output if that input violates the filter invariant.
The auto-generated AGREE specification states that only well-formed inputs are passed to the output.
The system developer must provide this filtering policy, but it is usually based on the existing assumptions made by downstream components that consume the filter output.

@@

The AGREE analysis of the cyber-hardened implementation with the auto-generated high-assurance components is shown in \figref{fig:hardened}.
Here AGREE provides a proof certificate that the high-assurance components guarantee the correct behavior of the SW implementation in the presence of the untrusted AI route planner.

@@

A similar proof is given for the synthesis of the contract model for a high-assurance component to CakeML.
A high-assurance component contract has a precise meaning in terms of data streams, and the synthesis exactly preserves that meaning in the generated code.
In other words, for any set of input streams that meet the component's contract assumptions, the output streams produced from the synthesized CakeML code exactly match those defined by the high-assurance component's contract.

Preserving the input to output relationship of streams between the two models lifts the contract verification results to the deployed system.
If the contract model verification succeeds, then the meaning of those results hold for the deployed system, given that all other components implement their contracts, an appropriate schedule exists that follows the dependent data-flow, and the communication fabric works as expected.

### 2022-03-14 paper/paper.tex
Revise example and add TODOs in all sections

% TODO: add in the referee tag for the submission
%\documentclass[global,twocolumn,referee]{svjour}
\documentclass[global,twocolumn]{svjour}
\usepackage{cite}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}

@@

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const}
}

@@

\newcommand{\figref}[1]{Fig.~\ref{#1}}

@@

\section{Introduction} \label{sec:intro}
\input{intro}
\subsection{SOSYM Journal Details}
The submission must have 30\% new material over what was published in MODELS 2021.
There is no page limit.
The article will go through a full review cycle.
The due date is \textbf{March} $1^\mathrm{st}$, \textbf{2022}.

\noindent The summary of the discussion regarding how the MODELS publication might be extended is given below.
\begin{compactitem}
  \item Expand the case study with the TA6 models
  \item Expand the case study with an actual full AGREE specification
  \item AGREE formal semantics summary including the uninterpreted functions
  \item Strengthen the assurance argument from AGREE to binary by way of CakeML
  \item Expand related work (add recent work published after 2018). 
  \item Respond more fully to the reviews from MODELS (see below).
\end{compactitem}

\noindent The summary of items from the MODELS reviews.
\begin{compactitem}
  \item Add recent work published after 2018
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
  \item Expand the role of Briefcase in the case study with input examples to provide more proof of the proposed model's effectiveness on the hardened system (e.g., show a malformed line search task, it's filter, and why it works) 
  \item Clarify research questions answered by the case study and make the figures bigger
  \item Discuss what efforts are optimized with the automations versus a fully manual process for creating the components--how does the automated transformation affect actual time for engineers
  \item Without verifying the correctness of the transformations, can prevention of certain attacks be guaranteed?
\end{compactitem}
\noindent Go to \url{https://mc.manuscriptcentral.com/sosym/}. Create a new account (if you don't have one), login and go to the "Author"-section, select the link "Start New Submission" under Author Dashboard and select "Special Section Paper" as the paper type, and choose "MODELS 2021 Special Issue". Also, make sure to mention the MODELS 2021 special issue in the cover letter.

\section{Simple Example} \label{sec:example}
\input{example}

@@

\section{Synthesis} \label{sec:synthesis}
\input{synthesis}

\section{UxAS Case Study} \label{sec:case-study}
\input{case-study}

@@

>>>>

% TODO: add in the referee tag for the submission
%\documentclass[global,twocolumn,referee]{svjour}
\documentclass[global,twocolumn]{svjour}
\usepackage{cite}
\usepackage{amsmath}
% \usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage[firstpage]{draftwatermark}
\usepackage[lighttt]{lmodern}
\usepackage[normalem]{ulem}

@@

\lstdefinestyle{agree}
{frame=none,
  basicstyle=\ttfamily,
  language=ML,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  numbers=none,
  numberstyle=\tiny\color{gray},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=true,
  tabsize=2,
  linewidth=2\linewidth,
  morekeywords={eq, bool, guarantee, assume, true, false, pre, not, and, or, property, const, Historically, Since, Once, event}
}

@@

\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\secref}[1]{Sec.~\ref{#1}}

@@

\section{Introduction} \label{sec:intro}
\input{intro}

\subsection{SOSYM Journal Details}
The due date is \textbf{March} $22^\mathrm{nd}$, \textbf{2022}.
Go to \url{https://mc.manuscriptcentral.com/sosym/}. Create a new account (if you don't have one), login and go to the "Author"-section, select the link "Start New Submission" under Author Dashboard and select "Special Section Paper" as the paper type, and choose "MODELS 2021 Special Issue". Also, make sure to mention the MODELS 2021 special issue in the cover letter.

\subsection{Revisions}
\begin{compactitem}
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
\end{compactitem}

\section{Illustrative Example} \label{sec:example}
\input{example}

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Reformat text to put single sentence on each line.}
  \item Move example to its own repository, archive, and give the DOI and URL for the example.
  \item \sout{Update AGREE certificates with new model}
  \item Separate example into separate files for initial design, cyber-components and tests, hardened design, and seL4 process design.
  \item \sout{Make clear the initial properties for the assumed correct model:}
    \begin{compactitem}
      \item \sout{Assume at the system level that a new automation request is not sent unless the prior request, if any, is acknowledged}
      \item \sout{Assume at all levels input messages are well-formed}
      \item \sout{Guarantee at all levels that waypoint outputs coincide with air vehicle location messages}
      \item \sout{Guarantee that a start from the waypoint manager coincides with an automation response}
      \item \sout{Guarantee for all trusted components that outputs are well-formed}
    \end{compactitem}
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item Add in the AGREE specification for the system
  \item Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)
\end{compactitem}

\section{AGREE Semantics for Component Synthesis}
\input{semantics}

\subsection{Revisions}
\begin{compactitem}
  \item Add in intuitive definition or AGREE leaf-component semantics
  \item State well-formed theorem
  \item State correctness theorem or any key theorems to the synthesis proof
\end{compactitem}

\section{Synthesis to CakeML and Proof Sketch} \label{sec:synthesis}
\input{synthesis}

\subsection{Revisions}
\begin{compactitem}
  \item State theorem relating the step function to the meaning of the leaf-node semantics
\end{compactitem}

\section{Case Studies} \label{sec:case-study}
\input{case-study}

\subsection{Revisions}
\begin{compactitem}
  \item Clarify research questions answered by the case study
  \item Make the figures bigger 
  \item Rewrite to focus on synthesized components and the AGREE specifications
  \item Add an interesting monitor from the TA6 model
  \item Discuss what efforts are optimized with the automations versus a fully manual process for creating the components--how does the automated transformation affect actual time for engineers
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item Add recent work published after 2018
\end{compactitem}
